### 2014-11-13 tex/intro.tex

The goal of this work is to mitigate the path explosion problem in GSE
by grouping multiple heaps together and only partitioning the heaps at
points of divergence in the control flow graph. Our inspiration is
found in the domain of static analysis that uses sets of constraints
over heap locations to encode multiple heaps in a single
representation. These sets, sometimes known as \emph{value sets} or
\emph{value summaries}, allow multiple heaps to be represented
simultaneously with a higher degree of precision than afforded by
traditional techniques for shape analysis. Some of these previous
attempts, however, are unable to handle aliasing in heaps due to a
recursive definition of objects~\cite{Xie:2005}, while others require
a set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static
analysis, over approximation of the heap representations alleviates
some of these limitations but often leads to infeasible heaps. Also,
heap updates require a rewrite of the constraint system making it
prohibtive for use in the context of symbolic execution.

\begin{comment}
Unfortunately, value sets often do not support aliasing and require a
recursive definition of objects~\cite{..}. Also, heap updates often
require that the path constraint be rewritten to reflect the update,
and the constraints in the value set may also need to be rewritten with the
addition of auxiliary variables. These non-local operations make it
difficult to use value sets in symbolic execution. As is
typical in static analysis, over approximation of the value sets
alleviates some of the limitations but also leads to false positives.
\end{comment}

%The goal of this work is find a more compact representation of the heaps
%and be better able to leverage constraint solvers.
%The  But any update of the heap required a rewrite on the constraint system
%or simply was not opssible to initialize and handle the aliasing possiblities.

%The goal is to leverage that

%Research in the abstract interpretation community has taken a very
%different approach to analyzing heap manipulating programs which
%computes a summary of possible heaps.  These techniques start with an
%initial heap configuration and then using a static analysis, make
%updates to the heap following program semantics, ultimately creating
%a heap summary which represents the potential heaps resulting from
%program execution~\cite{Dillig:2011}. Because these techniques are
%based on a static analysis, the heap summaries over-approximate the
%set of feasible heap configurations.

%The primary challenge relative to heap analysis for these techniques
%is to resolve potential dependencies of local results on the global
%aliases in the heap.  Recent work addresses these issues through
%strong updates to heap locations at call sites~\cite{Dillig} and
%computation of dangerous aliases~\cite{Matosevic}. Because these
%techniques are based on a static analysis, the resulting summaries
%over-approximate the actual potential heaps.

In this work, to effectively represent multiple heaps simultaneously
in the context of symbolic execution, we define a novel heap
representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, does not
require constraint rewriting on heap updates, and reduces
non-determinism in the search space during symbolic execution.

@@

The summary heap algorithm defines how the bipartite graph is updated
during lazy initialization. Unlike GSE, however, the summary heap
algorithm introduces non-determinism in the search only at points of
divergence in the control flow graph. These points of non-determinism
are at field accesses that lead to null-pointer exceptions
and at comparisons of references. The former represents a divergence
due to exceptional control flow while the latter is due to program
structure.

@@

This combination of summary heap and lazy initialization
enable us to improve the efficiency of symbolic execution of heap
manipulating programs over state-of-the-art techniques.
Furthermore, the summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation
between states in GSE and states in the summary heap algorithm. 
\begin{comment}
In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, and, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.
\end{comment}

@@

A preliminary implementation in Java Pathfinder (JPF) shows that in
general, the heap summary algorithm improves over other
state-of-the-art techniques, and in some instances, the improvement is
remarkable: two-orders of magnitude reduction in running time. More
critically though, the heap summary enables the initialization of
larger more complex heaps than previously possible as shown in our
results.

>>>>

The goal of this work is to mitigate the path explosion problem in GSE
by grouping multiple heaps together and only partitioning the heaps at
points of divergence in the control flow graph. Our inspiration is
found in the domain of static analysis that uses sets of constraints
over heap locations to encode multiple heaps in a single
representation. These sets, sometimes known as \emph{value sets} or
\emph{value summaries}, allow multiple heaps to be represented
simultaneously with a higher degree of precision than afforded by
traditional techniques for shape analysis. Some of these previous
attempts, however, are unable to handle aliasing in heaps due to a
recursive definition of objects~\cite{Xie:2005}, while others require
a set of heaps as input and are unable to initialize heaps
on-the-fly~\cite{Dillig:2011,Tillmann:2008}.  As is typical in static
analysis, over approximation of the heap representations alleviates
some of these limitations but often leads to infeasible heaps. Also,
most static analysis techniques for heap updates require a rewrite of
the constraint system making it prohibitive for use in the context of
symbolic execution.

In this work, to effectively represent multiple heaps simultaneously
in the context of symbolic execution, we define a novel heap
representation and an algorithm to initialize and update the heap
on-the-fly. In essence, our summary heap approach supports aliasing,
does not require constraint rewriting on heap updates, and reduces
non-determinism in the search space during symbolic execution.

@@

The summary heap algorithm defines how the bipartite graph is updated
during lazy initialization. Unlike GSE, however, the summary heap
algorithm introduces non-determinism in the search only at points of
divergence in the control flow graph. These points of non-determinism
are at field accesses that lead to null-pointer exceptions and at
comparisons of references. The former represents a divergence due to
exceptional control flow while the latter is due to program structure.
The combination of the heap representation and the summary heap
algorithm enables us to improve the efficiency of symbolic execution
of heap manipulating programs over state-of-the-art techniques.

@@

\begin{comment}
In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, and, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.
\end{comment}

@@

The summary heap algorithm is sound and complete with respect to
properties that are provable using GSE. This proof is accomplished by
showing the existence of a bisimulation between states in GSE and
states in the summary heap algorithm.  A preliminary implementation in
Java Pathfinder (JPF) shows that in general, the heap summary
algorithm improves over other state-of-the-art techniques, and in some
instances, the improvement is remarkable: two-orders of magnitude
reduction in running time. More importantly though, the heap summary
enables the initialization of larger more complex heaps than
previously possible as shown in our results.
